%===========================================================================
% Title: Safety Estimation: World Model Coordinates
% Authors: A. Tejada (Heavily edited version of Jeroen Ploeg's report. See bibliography.
% To be published in: for internal use only
% Date of submission:
% Date of submission R1:
% Date of submission R2:
%===========================================================================

\documentclass[10pt,final,letterpaper,oneside,onecolumn]{article}

%===========================================================================
% Packages
%===========================================================================
\usepackage[paper=letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry} % change page layout
\usepackage{amsfonts}
% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{multirow} % for tables
%\usepackage{cite} % for bibliography with biblatex
\usepackage{braket}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[style=ieee,doi=false,isbn=false,url=false,date=year,minbibnames=15,maxbibnames=15,backend=biber]{biblatex}
%\renewcommand*{\bibfont}{\footnotesize}		%% Use this for papers
\setlength{\biblabelsep}{\labelsep}
\bibliography{bibRiskPaper}
%\usepackage{subfig}
%\usepackage{amsthm}
%\usepackage{mathrsfs}
\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\graphicspath{ {figures/} }
\usepackage[capitalize]{cleveref}
\crefname{figure}{Figure}{Figures}
\usepackage{color}
\usepackage{units}
%\usepackage[English]{babel}             %% language support
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\usepackage{textcase}


%===========================================================================
% Miscellaneous
%===========================================================================
\graphicspath{{figures/}{more_figures/}}    % (graphicx) directory path for figures
%\interdisplaylinepenalty=2500              % (amsmath) allow for page breaks within multiline equations
%\numberwithin{equation}{section}           % (amsmath) include section number in equation numbering
%\numberwithin{figure}{section}             % (amsmath) include section number in figure numbering
%\numberwithin{table}{section}              % (amsmath) include section number in table numbering
%\addtolength{\arraycolsep}{-0.8mm}         % squeeze matrix columns a little
%\fnbelowfloat                               % (stfloats) put footnote below a float at the page bottom
%\bibliographystyle{unsrt}                   % (BibTeX) references style

% Switch off page numbering
\pagenumbering{gobble}

% For footnote in tabular
\usepackage{footnote}
\makesavenoteenv{tabular}
\makesavenoteenv{table}

% Tikz stuff
\usepackage{standalone}
\usepackage{tikz}
\usepackage{pgfplots}                           %% support for TikZ figures
%\usepackage{xcolor}
\usepackage{calc}
%\pgfplotsset{compat=1.16}
\usepgfplotslibrary{groupplots}
\newlength{\figurewidth}
\newlength{\figureheight}

\newlength\blockwidth
\newlength\blockheight
\newlength\blockx
\newlength\blocky
\setlength{\blockwidth}{8.5em}
\setlength{\blockheight}{4em}
\setlength{\blockx}{10em}
\setlength{\blocky}{7em}

% Table stuff
\usepackage{booktabs}
\setlength{\heavyrulewidth}{0.1em}
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}

% Reformat section titles
\usepackage[explicit]{titlesec}
\titleformat{\section}{}{}{1em}{\textbf{\MakeUppercase{\large{#1}}}}
\titleformat{\subsection}{}{}{1em}{\textbf{\large{#1}}}


\newcommand*{\ud}{\mathrm{\,d}}
\newcommand{\todo}[1]{\color{red}TODO: #1\color{black}}


%===========================================================================
% Begin document
%===========================================================================
\begin{document}

\noindent \MakeTextUppercase{\textbf{\large{A Method for Scenario Risk Quantification for Automated Driving Systems}}}\\

\noindent \textbf{Erwin de Gelder, Arash Khabbaz Saberi, Hala Elrofai}\\
\noindent TNO, Integrated Vehicle Safety Department\\
\noindent 5700 AT Helmond The Netherlands\\

\noindent Paper Number 19-0129\\

\noindent \textbf{\large{ABSTRACT}}\\

\noindent Recent innovations, such as automated driving and smart mobility, have elevated the safety-criticality of automotive systems due to the impact of these technologies on the traffic behavior and safety. New safety validation and assessment methodologies are required to provide the level of assurance that matches the societal impact of these systems.
The objective of this paper is to introduce a novel method for assessment and quantification of the risk of a driving scenario considering the operational design domain. 
For our proposed method, we assume that a scenario consists of activities (performed by different actors) and environmental conditions that leads to a potentially hazardous consequence.
The risk of a driving scenario is the product of the probability of the exposure of a scenario and the severity of the hazardous consequence of that scenario.
We introduce a systematic method for calculating the probability of exposure, 
where we assume a causal relation between the activities that constitute a scenario. 
By making educated assumptions on the dependencies among the different activities and environmental conditions, 
we simplify the calculation of the probability of the exposure. 
For estimating the severity, we employ Monte Carlo simulations.
% Results
We illustrate the use of our proposed method by applying it to an example of a collision avoidance system in a cut-in scenario.	
We use naturalistic driving data acquired from field studies on the Dutch highways to determine the risk. 
% Discussion and limitations
The presented example illustrates the potential of our proposed risk estimation method. 
% Conclusion
Using our proposed method, we can compare the safety criticality of various scenarios in a quantitative manner, which can be used as a safety metric for evaluating automated driving systems. 
This can lead to stronger justification for design decisions and test coverage for developing automated vehicle functionalities.


\pagebreak

\input{sections/introduction}
\input{sections/method}
\input{sections/example}
\input{sections/discussion}
\input{sections/conclusions}

% For some reason, I need \hspace to make sure that the title is also indented
\printbibliography[title=\hspace{7.5pt} References]


\end{document}
