%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document
\usepackage{amsfonts}
% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{multirow} % for tables
%\usepackage{cite} % for bibliography with biblatex
\usepackage{braket}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{breqn}
\usepackage[utf8]{inputenc}
\usepackage[style=ieee,doi=false,isbn=false,url=false,date=year,minbibnames=15,maxbibnames=15,backend=biber]{biblatex}
%\renewcommand*{\bibfont}{\footnotesize}		%% Use this for papers
\setlength{\biblabelsep}{\labelsep}
\bibliography{bibRiskPaper}
%\usepackage{subfig}
%\usepackage{amsthm}
%\usepackage{mathrsfs}
\usepackage{epsfig} % for postscript graphics files
\usepackage{nomencl}
%\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\graphicspath{ {figures/} }
\usepackage[capitalize]{cleveref}
\usepackage{color}
\usepackage{units}
%\usepackage[English]{babel}             %% language support
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}

% Tikz stuff
\usepackage{pgfplots}                           %% support for TikZ figures
\pgfplotsset{compat=1.16}
\usepgfplotslibrary{groupplots}
\newlength{\figurewidth}
\newlength{\figureheight}

% Table stuff
\usepackage{booktabs}
\setlength{\heavyrulewidth}{0.1em}
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}

\title{\LARGE \bf
A Method for Scenario Risk Quantification for Automated Driving Systems
}


\author{Arash Khabbaz Saberi, Erwin de Gelder, Hala Elrofai}
%\thanks{*This research has received funding from the European Unions Horizon 2020 research and innovation programme under ROADART Grant Agreement No 636565.}% <-this % stops a space
%\thanks{$^{1}$E. van Nunen is with the Department of Integrated Vehicle Safety, TNO, P.O.
%Box 756, 5700 AT Helmond, The Netherlands, and also with the Department of Mechanical Engineering, Eindhoven University of Technology, 5600 MB Eindhoven, The Netherlands


\begin{document}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
	
	
% Guideline: Context [DONE], Objective [DONE], Method, Results [DONE], Disccusion/limitations, Conclusion [DONE]. 

% Required by the ESV conference: Research Question/Objective [DONE], Methods and Data Sources, Results [DONE], Discussion and Limitations, Conclusion and relevance to session submitted 

% Left open: Method, Data Sources, Disussion and limitation, relevance. 

%TODO: Determine which track we want to go for
% Tuesday Afternoon Track C: Crash Avoidance: Automated Driving Systems (ADS) Levels 3, 4 and 5: Product Evolution; Evaluation; and Real-World Deployment Challenges
	
% Introduction
New developments in the automotive industry towards higher levels of automation are introducing new safety concerns for vehicles. 
Test procedures and performance measures need to be adapted for evaluation of vehicles with automated driving systems. 
With the increasing level of automation, the vehicle needs to operate safely in a large number of different scenarios. To assure the operational safety, the automated driving systems need to be assessed for this large number of scenarios. To prioritize the scenarios, risk assessment methods are required to estimate the associated risk for each scenario.
The state of the art risk assessment methods in the automotive domain, 
	such as the Hazard Analysis and Risk Assessment (HARA) of ISO~26262:2018, 
	have a qualitative nature and rely on expert's judgment for ranking the severity and probability of risks.
Moreover, these methods are only capable of evaluating the risk of a single (hazardous) event within the context of a generic operational situation.
The objective of this paper is to introduce a method for analysis and quantification of the risk of a driving scenario.

% Method
For the proposed method, we assume that a scenario consists of events, activities (performed by different actors), and environmental conditions.
Next, the risk of a driving scenario is considered as the product of severity of the outcome of a scenario and probability of the exposure of that scenario.
We introduce a systematic method for calculating this probability, 
	where we assume a causal relation between the activities and events that constitute a scenario. 
By making educated assumptions on the dependencies among the different activities, events, and environmental conditions, 
	we simplify the calculation of the probability of the exposure of a scenario. 
Finally, Monte Carlo simulations are employed for computing the risk of a scenario.


% Results
To illustrate the use of the proposed method, 
	we perform a case study by applying our proposed method for risk analysis of a cut-in scenario.	
We use naturalistic driving data acquired from field studies on the Dutch highways to determine the likelihoods of the events, activities, and environmental conditions that constitute the cut-in scenarios. Monte Carlo simulations are employed for determining the outcome of the cut-in scenarios, e.g., a collision or a near miss, given a state-of-the-art highway pilot system. 

% Discussion and limitations
The presented case study illustrates the potential of the proposed risk estimation method. The main limitation of the presented case study is the limited amount of data used. Furthermore, we applied the proposed method for only one type of driving scenario, while the full potential can be better demonstrated by applying the method to a wider range of scenarios.

% Conclusion
Using our proposed method, we can compare the safety criticality of various scenarios in a quantitative manner, which can be used as a safety metric for evaluating automated driving systems. 
This can lead to stronger justification for design decisions and test coverage for developing automated vehicle functionalities. 


%% No need to mention the challenges in the abstract
%%% Arash: This is required from the ESV to discuss the limitations. I think it's beacause this is more like an extended asbtact. 
% The challenge for applying this method is gathering enough data for quantification of scenario activities.
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{sections/introduction}
\input{sections/problem}
\input{sections/definitions}
\input{sections/method}
\input{sections/example}
\input{sections/discussion}
\input{sections/conclusions}





\section*{Acknowledgment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% When using biber:
\printbibliography

%% When using BibLaTeX:
%\bibliography{bibRiskPaper}
%\bibliographystyle{ieeetr}


\end{document}
