\section{Doctoral Education}
\label{sec:de}

The Doctoral Education (DE) program requires a total 45 GS credits. The total program is divided into three categories, i.e., research skills (\cref{sec:r skills}), discipline-related skills \cref{sec:d skills}), and transferable skills (\cref{sec:t skills}). A minimum of 15 GS credits is required for each category.

\subsection{Research skills}
\label{sec:r skills}

Research skills will help to reach full proficiency in conducting research. GS credits can be obtained by completing Learning-on-the-job activities. \Cref{tab:research skills} lists the Learning-on-the-job activities that are either completed or planned. All the activities up to Q3 2018 are completed, i.e., a total of 5 GS credits (out of 15 GC credits) are obtained at the time of writing this report.

\begin{table}[b]
	\centering
	\caption{Learning-on-the-job activities for obtaining the 15 GS credits for the research skills.}
	\label{tab:research skills}
	\begin{tabular}{lll}
		\toprule
		Learning-on-the-job activity & When & GS credits \\ \otoprule
		Paper review & Q1 2018 & 1 \\
		Writing first conference paper & Q1 2018 & 1 \\
		Paper review & Q1 2018 & 1 \\
		Addressing a small audience with presentation & Q2 2018 & 0.5 \\
		Addressing a major international audience with presentation & Q2 2018 & 1 \\
		Participation in work consultation with research partners & Q3 2018 & 0.5 \\
		Writing first journal paper & Q1 2019 & 3 \\
		Supervising MSc student & Q2 2019 & 4 \\
		Addressing a small audience with presentation & Q2 2019 & 0.5 \\
		Addressing a major international audience with presentation & Q2 2019 & 1 \\
		Poster presentation for small audience & Q2 2019 & 0.5 \\
		Addressing a major international audience with presentation & Q2 2020 & 1 \\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{Discipline-related skills}
\label{sec:d skills}

Discipline-related skills will improve the breadth of knowledge and, therefore, add to the quality of the doctoral research. No GC credits are earned yet. I will follow the MSc.\ course ``Applied statistics'' (6 ECTS) in the beginning of 2019. Other courses are not planned yet. The following courses might be useful regarding my PhD:
\begin{itemize}
	\item Uncertainty and sensitivity analysis (6 ECTS).
	\item Statistical learning for engineers (4 ECTS).
	\item Machine Learning (5 ECTS).
	\item Models in Software Engineering from the Institute for Programming research and Algorithmics (IPA).
	\item Introduction to R (winter course of the university of Leiden).
	\item Multilevel and Longitudinal Data Analysis (winter course of the university of Leiden).
\end{itemize}

\subsection{Transferable skills}
\label{sec:t skills}

Transferable skills helps to improve on a personal level. The PhD Start-up (2 GS credits) and Career Development (1 GS credit) are mandatory. The remaining 12 GC credits will be obtained by attending the following courses:
\begin{itemize}
	\item 3 GS credits, Q4 2018, Stakeholder management;
	\item 2.5 GS credits, Q2 2019, Effective negotiation: win-win communication;
	\item 2 GS credits, Q4 2019, Self-presentation: Confidence, focus and persuasion;
	\item 2 GS credits, Q2 2020, Communication, coping-strategies \& Awareness;
	\item 3 GS credits, Q4 2020, Writing a dissertation.
\end{itemize}
