\documentclass[10pt,final,a4paper,oneside,onecolumn]{article}

%%==========================================================================
%% Packages
%%==========================================================================
\usepackage[a4paper,left=3.5cm,right=3.5cm,top=3cm,bottom=3cm]{geometry} %% change page layout; remove for IEEE paper format
\usepackage[T1]{fontenc}                        %% output font encoding for international characters (e.g., accented)
\usepackage[cmex10]{amsmath}                    %% math typesetting; consider using the [cmex10] option
\usepackage{amssymb}                            %% special (symbol) fonts for math typesetting
\usepackage{amsthm}                             %% theorem styles
\usepackage{dsfont}                             %% double stroke roman fonts: the real numbers R: $\mathds{R}$
\usepackage{mathrsfs}                           %% formal script fonts: the Laplace transform L: $\mathscr{L}$
\usepackage[pdftex]{graphicx}                   %% graphics control; use dvips for TeXify; use pdftex for PDFTeXify
\usepackage{array}                              %% array functionality (array, tabular)
\usepackage{upgreek}                            %% upright Greek letters; add the prefix 'up', e.g. \upphi
\usepackage{stfloats}                           %% improved handling of floats
\usepackage{multirow}                           %% cells spanning multiple rows in tables
%\usepackage{subfigure}                         %% subfigures and corresponding captions (for use with IEEEconf.cls)
\usepackage{subfig}                             %% subfigures (IEEEtran.cls: set caption=false)
\usepackage{fancyhdr}                           %% page headers and footers
\usepackage[official,left]{eurosym}             %% the euro symbol; command: \euro
\usepackage{appendix}                           %% appendix layout
\usepackage{xspace}                             %% add space after macro depending on context
\usepackage{verbatim}                           %% provides the comment environment
\usepackage[dutch,USenglish]{babel}             %% language support
\usepackage{wrapfig}                            %% wrapping text around figures
\usepackage{longtable}                          %% tables spanning multiple pages
\usepackage{pgfplots}                           %% support for TikZ figures (Matlab/Python)
\pgfplotsset{compat=1.14}						%% Run in backwards compatibility mode
\usepackage[breaklinks=true,hidelinks,          %% implement hyperlinks (dvips yields minor problems with breaklinks;
bookmarksnumbered=true]{hyperref}   %% IEEEtran: set bookmarks=false)
%\usepackage[hyphenbreaks]{breakurl}            %% allow line breaks in URLs (don't use with PDFTeX)
\usepackage[final]{pdfpages}                    %% Include other pdfs
\usepackage[capitalize]{cleveref}				%% Referensing to figures, equations, etc.
\usepackage{units}								%% Appropriate behavior of units


\pagestyle{fancy}                                       %% set page style
\fancyhf{}                                              %% clear all header & footer fields
\renewcommand*{\headrulewidth}{0pt}                  	%% No line in this case

\newcommand{\expectation}[1]{\textup{E} \left[ #1 \right]}
\newcommand{\mise}[2]{\textup{MISE}_{#1}\left( #2 \right)}
\newcommand{\amise}[2]{\textup{AMISE}_{#1} \left( #2 \right)}
\newcommand{\measure}[2]{J_{#1} \left( #2 \right)}
\newcommand*{\ud}{\mathrm{\,d}}

\usepackage{titlesec}
\titlespacing*{\paragraph}{0ex}{1ex}{1ex}
\newcommand{\toauthor}{\paragraph*{Comment to author:}}
\newcommand{\fromauthor}{\paragraph*{Comment from author:}}

\begin{document}
	
\section*{Cover letter}

This cover letter describes how we have addressed the reviewers' comments. Any changes to the paper are shown in \color{red}red\color{black}. Furthermore, a gray bar is shown next to the updated parts.
	
\section*{Review 1}

\toauthor The issue is relevant to a broad audience but the article is addressing a limited group because of the necessary and complicated maths. Consider to shorten parts of section IV on examples in favor of the discussion. 

\fromauthor The discussion is expanded. Furthermore, some text is added to the method section to help the reader interpreting the maths.

\toauthor For instance, braking seems a relatively simple activity but the method does not allow for full stops.

\fromauthor A note is added to the first paragraph of Section IV-B.

\toauthor chosen parameters are (clearly) dependent and thus the outcome shows that for an accurate completeness many samples are needed. 

\fromauthor In fact, the average deceleration is hardly dependent on the other parameters. This is mentioned in the paper by the sentence ``Note that the correlation between the average deceleration and the other parameters is fairly low, so this justifies this choice.''

\toauthor But what sort of threshold is needed? Why 0.003? 

\fromauthor This is addressed in the second paragraph of the discussion.

\toauthor Any idea (rough estimate) how many hours ND is enough for a 'naturalistic' driver behavior model that will improve micro-simulations drastically or what sort of activities are likely to be modeled (i.e. complete) accurately because they happen a lot (like braking), don't need many (or complex) parameters and which activities are rare, diverse and therefore need large ND mileages? Maybe it is far too early to tell, but that would be an answer as well. 

\fromauthor Some text is added to the discussion's last paragraph to elaborate on this.

\section*{Review 2}

\toauthor This is an interesting paper on statistical methodology. If I understand it correctly, it is similar to the usual sample size formulae necessary for given precision of parameter estimates or power of statistical tests -- with the extension to a desired description of the 'complete' probability distribution. Typically, extensions of methodology to more complicated situations (e.g., multivariate vs. univariate) are justified by showing that the general formulae simplify to the more familiar form in special cases. Is that the case for this methodology? Suppose the pdf was Bernoulli? 

\toauthor In the current paper, it is assumed that the probability density function (pdf) is estimated using kernel density estimation (KDE), regardless of the underlying distribution. Hence, even if the underlying distribution is as simple as, for example, a uniform distribution (let us assume a continuous distribution), the same formulas apply. The only way to simplify the measure for completeness is by assuming a univariate distribution. In that case, 
\begin{equation}
	\measure{f}{n} = \frac{h^4}{4} \sigma_K^4 \int_{\mathbb{R}^d} \left( \nabla^2 \hat{f}(x;n) \right)^2 \ud x + \frac{\mu_K}{nh^d}.
\end{equation}
simplifies to
\begin{equation}
	\measure{f}{n} = \frac{h^4}{4} \sigma_K^4 \int_{-\infty}^{\infty} \left( \frac{\ud^2 f(x)}{\ud x^2} \right)^2 \ud x + \frac{\mu_K}{nh}.
\end{equation}
As this is not considered as a major simplification, this is omitted from the paper.

\toauthor The title of the paper is a bit misleading, as you state in the discussion that the desired threshold for completeness will require more application-specific research. A better title would be `How do we determine if we've collected enough field data?'

\fromauthor We changed the title accordingly.

\section*{Review 3}

\toauthor It's a very interesting concept. You are correct in that the notion of ``enough'' data relies very heavily upon the goal of the use of the data. For example, the crash scenarios/typology may be sufficient for proving safety equivalence or passing a minimum set of regulations, but when designing systems to consider edge cases, is there ever really ``enough'' data? 

\fromauthor A note is added to the second paragraph of the discussion (Section~V) to explain that only infinite data results in the measure for completeness to approach zero.

\section*{Review 4}

\toauthor In the paper, the author proposed a method to decide whether enough field data is collected. The topic is very important, and the paper was well constructed. The paper can be further improved by considering the following:

1. The basis of the paper is built on the ``scenario''. It will make the paper more complete if the concept and the way to obtain scenario is first discussed - either defined directly by experts or extracted through unsupervised learning.

\fromauthor Few references are given when introducing the concept of scenario (Section~II).

\toauthor 2. How to justify the example given in this paper is a good representation of the proposed method? How sensitive is the conclusion to different criteria? More statistical analysis is appreciated.

\fromauthor A paragraph is added to the discussion to elaborate on some considerations when employing our measure for completeness. 


\end{document}