\begin{abstract}

The safety assessment of \acp{av} is an important aspect of the development cycle of \acp{av}.
A scenario-based assessment approach is accepted by many players in the field as part of the complete safety assessment.
One way to generate the required scenario-based test descriptions is to parameterize the scenarios and to draw these parameters from \iac{pdf}.
\cstarta A scenario is a representation of a situation on the road to which the \ac{av} needs to respond appropriately.
Because the shape of the \ac{pdf} is unknown beforehand, assuming a functional form of the \ac{pdf} and fitting the parameters to the data may lead to inaccurate fits.
As an alternative, \ac{kde} is a promising candidate for estimating the underlying \ac{pdf}, because it is flexible with the underlying distribution of the parameters. \cenda
Drawing random samples from \iac{pdf} estimated with \ac{kde} is possible without the need of evaluating the actual \ac{pdf}, which makes it suitable for drawing random samples for, e.g., Monte Carlo methods.
\cstarta Sampling from \iac{kde} while the samples satisfy linear equality constraints, however, has not been described in the literature, as far as the authors know. \cenda

In this paper, we provide a method to sample from a conditional \ac{pdf} in case the \ac{pdf} is estimated using \ac{kde}. 
Besides, we propose a method to sample from \iac{pdf} estimated using \ac{kde}, such that the samples satisfy linear equality constraints. 
We also present the algorithms of our method in pseudo-code. 
Furthermore, through an example, we illustrate the performance of the presented method by generating braking scenarios that have, e.g., a predetermined starting speed.
Because our method does not evaluate the actual (conditional) \ac{pdf}, it is efficient in terms of computational costs.

\end{abstract}
