\begin{abstract}
	% Explain issue: assessment is important
	The development of \cstartd new \cendd assessment methods for the performance of \acp{av} is essential to enable the deployment of automated driving technologies, due to the complex operational domain of \acp{av}.
	% Introduce scenarios (for assessment)
	\cstarte One contributing method \cende\cstartd is scenario-based assessment in which test cases are derived from real-world road traffic scenarios obtained from driving data. \cendd
	% Problem -> definition needed for scenario
	\cstarte Given the complexity of the reality that is being modeled in these scenarios, it is a challenge to know when enough information is captured in the scenario for defining an effective test case. Dependent on the situation, the critical parameters that are needed in a particular scenario differs. This fact makes it difficult to define a structure for capturing these scenarios. \cende
	\cstartc An intensional definition that provides a set of characteristics that are deemed to be both necessary and sufficient to qualify as a scenario assures that the scenarios constructed are both complete and intercomparable.
	
	% Solution: concrete definitions
	In this paper, we develop a comprehensive and operable definition of \cendc\cstartd the notion of scenario while considering \cendd\cstartc existing definitions in the literature.
	This is achieved by proposing an \ac{oof} in which a scenario and its building blocks are defined as classes of objects having attributes, methods, and relationships with other objects.
	We also introduce the concept of a scenario category that enables the categorization of scenarios in terms of the categories of their typical components.
	% Benefits of our approach
	The object-oriented approach promotes clarity, modularity, reusability, and encapsulation of the objects. 
	We provide definitions and justifications of each of the terms
	Furthermore, the \ac{oof} is used to translate the terms in a coding language that is publicly available. \cendc
	% Example
	An example illustrates that the presented \cstartb framework \cendb is applicable for scenario-based assessment of \acp{av}.
\end{abstract}
