\section{Problem formulation}
\label{sec:problem}

To formulate the risk quantification problem, we distinguish quantitative scenarios from qualitative scenarios, using the definitions of \emph{scenario} and \emph{scenario category} of \autocite{degelder2018ontology}:

\begin{definition}[Scenario]
	\label{def:scenario}
	A scenario is a quantitative description of the relevant characteristics of the ego vehicle, its activities and/or goals, its static environment, and its dynamic environment. In addition, a scenario contains all events that are relevant to the ego vehicle.
\end{definition}

\begin{definition}[Scenario category]
	\label{def:scenario category}
	A scenario category is a qualitative description of the ego vehicle, its activities and/or goals, its static environment, and its dynamic environment.
\end{definition}

A scenario category is an abstraction of a scenario and, therefore, a scenario category comprises multiple scenarios \autocite{degelder2018ontology}.
For example, the scenario category ``cut-in'' comprises all possible cut-in scenarios. 
Given such a scenario category, our goal is to find all corresponding scenarios in a given data set. 

The main objective of this paper is to quantify the risk of a system-under-test when operating in all possible scenarios comprised by a given scenario category. The focus is on the system-under-test itself, its occupants, and its direct surroundings. Hence, we define the risk quantification problem as follows:

\begin{problem}[Risk quantification]
	\label{problem:risk quantification}
	Given a scenario category, how to quantify the risk on vehicle level?
\end{problem}

Risk is typically a combination of the likelihood and the severity of any harm. In our case, the likelihood of any harm can be decomposed in two components: the likelihood of a scenario of the given scenario category and the likelihood of any harm if such a scenario occurs. Based on this observation, we can divide \cref{problem:risk quantification} into three sub-problems:

\begin{problem}[Exposure]
	\label{problem:exposure}
	Given a scenario category, how to find all scenarios that correspond to this scenario category in a given data set?
\end{problem}

\begin{problem}[Harm likelihood]
	\label{problem:controllability}
	Given a scenario category and a system-under-test, how to estimate the likelihood of any harm?
\end{problem}

\begin{problem}[Severity]
	\label{problem:severity}
	Given a scenario category, a system-under-test, and a possible harmful outcome, how to estimate the severity of that harm?
\end{problem}
